### 2019-04-07 chapters/3-results.tex
tables adjusted
figures location: !h -> !ht
table captions better

\begin{table}[!h]
  \centering
  \caption{{\bf Texture methods ranked in the best one percent.}}%
  \label{tab:texture_best1p}

  \begin{tabular}{c c c c}
  \hline
  Image type & Window sizes & Texture extraction methods & AUC range \\
  \hline
  T₂w & 27 & MBB-GLCM, GLCM, Gabor & 0.71--0.84 \\
  ADCₘ & 11 & Gabor & 0.79--0.80 \\
  ADCₖ & 11 & Gabor & 0.79--0.80 \\
  K & 7, 9 & Zernike, Gabor & 0.78--0.83 \\
  T₂ & 15, 19, 27, 31, 35 & Zernike, Hu, MBB-GLCM, LBP, GLCM, Gabor & 0.71--0.75 \\
  \hline
  \end{tabular}
\end{table}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=1.0\textwidth]{figures/fig3}
    \caption{{\bf An example of texture feature maps.}
    These are extracted from DWI parametric maps (ADCₘ, ADCₖ, K), T₂-weighted
    imaging (T₂w), and parametric map of T₂ relaxation values (T₂). Source image
    type, window size, and texture descriptor parameters are shown above the
    images. The two lesions are outlined; their Gleason scores are 4+3 (lower)
    and 3+4 (upper).}%
    \label{fig:tmap}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=1.0\textwidth]{figures/fig4}
    \caption{{\bf ROC curves within each image type (T₂w, ADCₘ, ADCₖ, K, T₂).}
    A:~The best statistical feature. B:~The best texture feature. The final
    model of the best selected features from ADCₘ, K, and T₂w obtained using L1
    regularized logistic regression and validated with leave-pair-out
    cross-validation (LPOCV) is also included in both A and B.}%
    \label{fig:roc}
\end{figure}

@@

\begin{table}[!h]
  \centering
  \caption{{\bf Area under the receiver operating curve values estimated using
  outer leave-pair-out cross-validation (LPOCV) per image type with all
  features, top 1\% features filtered by AUC, and the 18 statistical
  features.}}%
  \label{tab:auc_imagetype}

  %\begin{tabular}{p{3em} p{5.2em} | p{3em} p{7.2em} | p{5.7em} p{7.2em} | p{7.2em}}
  \begin{tabular}{c c  c c  c c  c}
  \hline
  & & \multicolumn{2}{c}{All features} & \multicolumn{2}{c}{Top 1\% features} & 18 statistical \\
  Image type & ML algorithm & N & AUC \ci{95\%~CI} & N & AUC \ci{95\%~CI} & AUC \ci{95\%~CI} \\
  \hline
  T₂w  & Log. Reg. L1 & 1631 & 0.82 \ci{0.72--0.92} & 16 & 0.80 \ci{0.69--0.90} & 0.67 \ci{0.56--0.77} \\
       & Log. Reg. L2 &      & 0.68 \ci{0.55--0.82} &    & 0.75 \ci{0.64--0.87} & 0.71 \ci{0.60--0.81} \\
  ADCₘ & Log. Reg. L1 & 1281 & 0.67 \ci{0.55--0.79} & 12 & 0.71 \ci{0.60--0.82} & 0.79 \ci{0.68--0.90} \\
       & Log. Reg. L2 &      & 0.69 \ci{0.57--0.81} &    & 0.75 \ci{0.65--0.86} & 0.75 \ci{0.63--0.86} \\
  ADCₖ & Log. Reg. L1 & 1281 & 0.71 \ci{0.58--0.83} & 12 & 0.74 \ci{0.63--0.84} & 0.78 \ci{0.69--0.88} \\
       & Log. Reg. L2 &      & 0.73 \ci{0.63--0.83} &    & 0.76 \ci{0.65--0.86} & 0.73 \ci{0.61--0.84} \\
  K    & Log. Reg. L1 & 1281 & 0.64 \ci{0.52--0.77} & 12 & 0.78 \ci{0.67--0.89} & 0.75 \ci{0.61--0.88} \\
       & Log. Reg. L2 &      & 0.73 \ci{0.60--0.85} &    & 0.76 \ci{0.64--0.87} & 0.73 \ci{0.60--0.86} \\
  T₂   & Log. Reg. L1 & 1631 & 0.58 \ci{0.45--0.71} & 16 & 0.51 \ci{0.37--0.65} & 0.67 \ci{0.55--0.79} \\
       & Log. Reg. L2 &      & 0.70 \ci{0.59--0.82} &    & 0.56 \ci{0.43--0.69} & 0.56 \ci{0.43--0.68} \\
  \hline
  \end{tabular}
\end{table}

@@

\begin{table}[!h]
  \centering
  \caption{{\bf Area under the receiver operating curve values estimated using
  outer leave-pair-out cross-validation (LPOCV) for the combinations of the
  image types.}}%
  \label{tab:auc_combinations}

  %\begin{tabular}{l p{5.2em} p{3em} p{7.2em} p{5.7em} p{7.2em}}
  \begin{tabular}{c c  c c  c c}
  \hline
  & & \multicolumn{2}{c}{All features} & \multicolumn{2}{c}{Top 1\% features} \\
  Image types & ML algorithm & N & AUC \ci{95\%~CI} & N & AUC \ci{95\%~CI} \\
  \hline
  ADCₖ, K                & Log. Reg. L1 & 2562 & 0.61 \ci{0.49--0.74} & 25 & 0.82 \ci{0.72--0.92} \\
                         & Log. Reg. L2 &      & 0.72 \ci{0.60--0.83} &    & 0.81 \ci{0.70--0.91} \\
  ADCₘ, K                & Log. Reg. L1 & 2562 & 0.57 \ci{0.45--0.70} & 25 & 0.81 \ci{0.71--0.91} \\
                         & Log. Reg. L2 &      & 0.72 \ci{0.60--0.84} &    & 0.79 \ci{0.68--0.89} \\
  ADCₘ, ADCₖ, K          & Log. Reg. L1 & 3843 & 0.58 \ci{0.44--0.72} & 38 & 0.83 \ci{0.74--0.92} \\
                         & Log. Reg. L2 &      & 0.69 \ci{0.56--0.81} &    & 0.79 \ci{0.70--0.88} \\
  ADCₘ, ADCₖ, K, T₂      & Log. Reg. L1 & 5474 & 0.61 \ci{0.47--0.74} & 54 & 0.84 \ci{0.75--0.92} \\
                         & Log. Reg. L2 &      & 0.77 \ci{0.66--0.87} &    & 0.79 \ci{0.70--0.88} \\
  ADCₘ, ADCₖ, K, T₂w     & Log. Reg. L1 & 5474 & 0.78 \ci{0.68--0.89} & 54 & 0.88 \ci{0.81--0.95} \\
                         & Log. Reg. L2 &      & 0.70 \ci{0.58--0.82} &    & 0.86 \ci{0.78--0.93} \\
  ADCₘ, ADCₖ, K, T₂, T₂w & Log. Reg. L1 & 7105 & 0.74 \ci{0.62--0.86} & 71 & 0.88 \ci{0.81--0.95} \\
                         & Log. Reg. L2 &      & 0.79 \ci{0.69--0.90} &    & 0.86 \ci{0.78--0.93} \\
  ADCₘ, K, T₂            & Log. Reg. L1 & 4193 & 0.69 \ci{0.56--0.82} & 41 & 0.83 \ci{0.74--0.91} \\
                         & Log. Reg. L2 &      & 0.78 \ci{0.68--0.88} &    & 0.82 \ci{0.73--0.90} \\
  ADCₘ, K, T₂w           & Log. Reg. L1 & 4193 & 0.81 \ci{0.71--0.91} & 41 & 0.88 \ci{0.82--0.95} \\
                         & Log. Reg. L2 &      & 0.70 \ci{0.59--0.82} &    & 0.86 \ci{0.79--0.93} \\
  ADCₘ, K, T₂, T₂w       & Log. Reg. L1 & 5824 & 0.76 \ci{0.65--0.87} & 58 & 0.87 \ci{0.81--0.94} \\
                         & Log. Reg. L2 &      & 0.79 \ci{0.68--0.89} &    & 0.85 \ci{0.77--0.92} \\
  ADCₖ, K, T₂            & Log. Reg. L1 & 4193 & 0.53 \ci{0.40--0.66} & 41 & 0.81 \ci{0.72--0.91} \\
                         & Log. Reg. L2 &      & 0.80 \ci{0.71--0.89} &    & 0.81 \ci{0.71--0.91} \\
  ADCₖ, K, T₂w           & Log. Reg. L1 & 4193 & 0.81 \ci{0.72--0.91} & 41 & 0.85 \ci{0.77--0.93} \\
                         & Log. Reg. L2 &      & 0.72 \ci{0.61--0.84} &    & 0.84 \ci{0.76--0.92} \\
  T₂, T₂w                & Log. Reg. L1 & 3262 & 0.82 \ci{0.73--0.91} & 32 & 0.66 \ci{0.52--0.79} \\
                         & Log. Reg. L2 &      & 0.78 \ci{0.68--0.88} &    & 0.61 \ci{0.48--0.74} \\
  \hline
  \end{tabular}
\end{table}

>>>>

\begin{table}[!h]
\begin{adjustwidth}{-2.25in}{0in}
\centering
\caption{{\bf Texture methods ranked in the best one percent.}}%
\label{tab:texture_best1p}

\begin{tabular}{c c c c}
\hline
Image type & Window sizes & Texture extraction methods & AUC range \\
\hline
T₂w & 27 & MBB-GLCM, GLCM, Gabor & 0.71--0.84 \\
ADCₘ & 11 & Gabor & 0.79--0.80 \\
ADCₖ & 11 & Gabor & 0.79--0.80 \\
K & 7, 9 & Zernike, Gabor & 0.78--0.83 \\
T₂ & 15, 19, 27, 31, 35 & Zernike, Hu, MBB-GLCM, LBP, GLCM, Gabor & 0.71--0.75 \\
\hline
\end{tabular}
\end{adjustwidth}
\end{table}

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=1.0\textwidth]{figures/fig3}
    \caption{{\bf An example of texture feature maps.}
    These are extracted from DWI parametric maps (ADCₘ, ADCₖ, K), T₂-weighted
    imaging (T₂w), and parametric map of T₂ relaxation values (T₂). Source image
    type, window size, and texture descriptor parameters are shown above the
    images. The two lesions are outlined; their Gleason scores are 4+3 (lower)
    and 3+4 (upper).}%
    \label{fig:tmap}
\end{figure}

\begin{figure}[!ht]
    \centering
    \includegraphics[width=1.0\textwidth]{figures/fig4}
    \caption{{\bf ROC curves within each image type (T₂w, ADCₘ, ADCₖ, K, T₂).}
    A:~The best statistical feature. B:~The best texture feature. The final
    model of the best selected features from ADCₘ, K, and T₂w obtained using L1
    regularized logistic regression and validated with leave-pair-out
    cross-validation (LPOCV) is also included in both A and B.}%
    \label{fig:roc}
\end{figure}

@@

\begin{table}[!h]
\begin{adjustwidth}{-2.25in}{0in}
\centering
%\caption{{\bf Area under the receiver operating curve values estimated using
%outer leave-pair-out cross-validation (LPOCV) per image type with all
%features, top 1\% features filtered by AUC, and the 18 statistical
%features.}}%
\caption{{\bf Performance figures for each image type alone.} They are ROC AUC
(receiver operating characteristic, area under curve) values estimated using
outer leave-pair-out cross-validation (LPOCV) and different feature subsets.}%
\label{tab:auc_imagetype}

%\begin{tabular}{p{3em} p{5.2em} | p{3em} p{7.2em} | p{5.7em} p{7.2em} | p{7.2em}}
\begin{tabular}{c c  c c  c c  c}
\hline
& & \multicolumn{2}{c}{All features} & \multicolumn{2}{c}{Top 1\% features} & 18 statistical \\
Image type & ML algorithm & N & AUC \ci{95\%~CI} & N & AUC \ci{95\%~CI} & AUC \ci{95\%~CI} \\
\hline
T₂w  & Log. Reg. L1 & 1631 & 0.82 \ci{0.72--0.92} & 16 & 0.80 \ci{0.69--0.90} & 0.67 \ci{0.56--0.77} \\
     & Log. Reg. L2 &      & 0.68 \ci{0.55--0.82} &    & 0.75 \ci{0.64--0.87} & 0.71 \ci{0.60--0.81} \\
ADCₘ & Log. Reg. L1 & 1281 & 0.67 \ci{0.55--0.79} & 12 & 0.71 \ci{0.60--0.82} & 0.79 \ci{0.68--0.90} \\
     & Log. Reg. L2 &      & 0.69 \ci{0.57--0.81} &    & 0.75 \ci{0.65--0.86} & 0.75 \ci{0.63--0.86} \\
ADCₖ & Log. Reg. L1 & 1281 & 0.71 \ci{0.58--0.83} & 12 & 0.74 \ci{0.63--0.84} & 0.78 \ci{0.69--0.88} \\
     & Log. Reg. L2 &      & 0.73 \ci{0.63--0.83} &    & 0.76 \ci{0.65--0.86} & 0.73 \ci{0.61--0.84} \\
K    & Log. Reg. L1 & 1281 & 0.64 \ci{0.52--0.77} & 12 & 0.78 \ci{0.67--0.89} & 0.75 \ci{0.61--0.88} \\
     & Log. Reg. L2 &      & 0.73 \ci{0.60--0.85} &    & 0.76 \ci{0.64--0.87} & 0.73 \ci{0.60--0.86} \\
T₂   & Log. Reg. L1 & 1631 & 0.58 \ci{0.45--0.71} & 16 & 0.51 \ci{0.37--0.65} & 0.67 \ci{0.55--0.79} \\
     & Log. Reg. L2 &      & 0.70 \ci{0.59--0.82} &    & 0.56 \ci{0.43--0.69} & 0.56 \ci{0.43--0.68} \\
\hline
\end{tabular}
\end{adjustwidth}
\end{table}

@@

\begin{table}[!h]
\begin{adjustwidth}{-2.25in}{0in}
\centering
%\caption{{\bf Area under the receiver operating curve values estimated using
%outer leave-pair-out cross-validation (LPOCV) for the combinations of the
%image types.}}%
\caption{{\bf Performance figures for image type combinations.} They are ROC AUC
(receiver operating characteristic, area under curve) values estimated using
outer leave-pair-out cross-validation (LPOCV) and different feature subsets.}%
\label{tab:auc_combinations}

%\begin{tabular}{l p{5.2em} p{3em} p{7.2em} p{5.7em} p{7.2em}}
\begin{tabular}{c c  c c  c c}
\hline
& & \multicolumn{2}{c}{All features} & \multicolumn{2}{c}{Top 1\% features} \\
Image types & ML algorithm & N & AUC \ci{95\%~CI} & N & AUC \ci{95\%~CI} \\
\hline
ADCₖ, K                & Log. Reg. L1 & 2562 & 0.61 \ci{0.49--0.74} & 25 & 0.82 \ci{0.72--0.92} \\
                       & Log. Reg. L2 &      & 0.72 \ci{0.60--0.83} &    & 0.81 \ci{0.70--0.91} \\
ADCₘ, K                & Log. Reg. L1 & 2562 & 0.57 \ci{0.45--0.70} & 25 & 0.81 \ci{0.71--0.91} \\
                       & Log. Reg. L2 &      & 0.72 \ci{0.60--0.84} &    & 0.79 \ci{0.68--0.89} \\
ADCₘ, ADCₖ, K          & Log. Reg. L1 & 3843 & 0.58 \ci{0.44--0.72} & 38 & 0.83 \ci{0.74--0.92} \\
                       & Log. Reg. L2 &      & 0.69 \ci{0.56--0.81} &    & 0.79 \ci{0.70--0.88} \\
ADCₘ, ADCₖ, K, T₂      & Log. Reg. L1 & 5474 & 0.61 \ci{0.47--0.74} & 54 & 0.84 \ci{0.75--0.92} \\
                       & Log. Reg. L2 &      & 0.77 \ci{0.66--0.87} &    & 0.79 \ci{0.70--0.88} \\
ADCₘ, ADCₖ, K, T₂w     & Log. Reg. L1 & 5474 & 0.78 \ci{0.68--0.89} & 54 & 0.88 \ci{0.81--0.95} \\
                       & Log. Reg. L2 &      & 0.70 \ci{0.58--0.82} &    & 0.86 \ci{0.78--0.93} \\
ADCₘ, ADCₖ, K, T₂, T₂w & Log. Reg. L1 & 7105 & 0.74 \ci{0.62--0.86} & 71 & 0.88 \ci{0.81--0.95} \\
                       & Log. Reg. L2 &      & 0.79 \ci{0.69--0.90} &    & 0.86 \ci{0.78--0.93} \\
ADCₘ, K, T₂            & Log. Reg. L1 & 4193 & 0.69 \ci{0.56--0.82} & 41 & 0.83 \ci{0.74--0.91} \\
                       & Log. Reg. L2 &      & 0.78 \ci{0.68--0.88} &    & 0.82 \ci{0.73--0.90} \\
ADCₘ, K, T₂w           & Log. Reg. L1 & 4193 & 0.81 \ci{0.71--0.91} & 41 & 0.88 \ci{0.82--0.95} \\
                       & Log. Reg. L2 &      & 0.70 \ci{0.59--0.82} &    & 0.86 \ci{0.79--0.93} \\
ADCₘ, K, T₂, T₂w       & Log. Reg. L1 & 5824 & 0.76 \ci{0.65--0.87} & 58 & 0.87 \ci{0.81--0.94} \\
                       & Log. Reg. L2 &      & 0.79 \ci{0.68--0.89} &    & 0.85 \ci{0.77--0.92} \\
ADCₖ, K, T₂            & Log. Reg. L1 & 4193 & 0.53 \ci{0.40--0.66} & 41 & 0.81 \ci{0.72--0.91} \\
                       & Log. Reg. L2 &      & 0.80 \ci{0.71--0.89} &    & 0.81 \ci{0.71--0.91} \\
ADCₖ, K, T₂w           & Log. Reg. L1 & 4193 & 0.81 \ci{0.72--0.91} & 41 & 0.85 \ci{0.77--0.93} \\
                       & Log. Reg. L2 &      & 0.72 \ci{0.61--0.84} &    & 0.84 \ci{0.76--0.92} \\
T₂, T₂w                & Log. Reg. L1 & 3262 & 0.82 \ci{0.73--0.91} & 32 & 0.66 \ci{0.52--0.79} \\
                       & Log. Reg. L2 &      & 0.78 \ci{0.68--0.88} &    & 0.61 \ci{0.48--0.74} \\
\hline
\end{tabular}
\end{adjustwidth}
\end{table}
